---
title: "Assigment - kNN DIY"
author:
  - Luc Heimans - Author
  - Daan Plass - Reviewer
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---


```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

---

Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train  your own kNN model. Follow all the steps from the CRISP-DM model.

```{r}
Rawd <- read.csv("https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-occupancy.csv")
```


## Business Understanding
The business case in this instance is to experiment with the KNN machine learning methodology, following the CRISP DM model. The goal is to, as accurately as possible, predict the value of a label, based on KNN learning. In this case I will try to classify the value of the label; occupancy as accurately as possible, using KNN methodology.

## Data Understanding
In this step I will explore the data set to become familiar with the data and understand its structure.

What becomes clear is that I will be dealing with structured data. Furthermore, occupancy consists of integer values. Data consists of characters and the remaining variables are numerical.

```{r}
str(Rawd)
head(Rawd)
```

Since the label is occupancy in this case, I would like to also explore the relationships between outcomes.

```{r}
cntRawd <- table(Rawd$Occupancy)
propRawd <- round(prop.table(cntRawd)*100, digits = 1)

print(cntRawd)
print(propRawd)
```

What becomes clear is that occupancy with a value of 0 is 79% more common than a value of 1.

## Data Preparation

In this step I will clean the data to remain with values that are of value to classifying new data.
The variable 'date' is not of relevance in creating a model which should predict the label; occupancy, and thus will be removed from the dataset.

```{r}
cleand <- Rawd[-1]
head(cleand)
```

I will also search for possible N/A values.

```{r}
indx <- apply(cleand, 2, function(cleand) any(is.na(cleand)))
colnames(indx)
```

Colnames command answers "NULL", meaning there are no values in any of the columns which consist of N/A.

Additionally, I want to check if there is a need for standardization of the values. I will do this by checking a summary of each variable (except the label) to see if there is a potential outlier which could influence the outcome too significantly. 

```{r}
summary(Rawd[c("Temperature", "Humidity", "Light", "CO2", "HumidityRatio")])
```
There is a clear need for standardization since 'Light', 'CO2' and 'HumidityRatio' have very different means compared to 'Temperature' and 'Humidity'.

```{r}

```


## Modeling
text and code here

## Evaluation and Deployment
text and code here

reviewer adds suggestions for improving the model